MaxEnt: What is it good for?

### 2015-06-26 ms.tex
New figure
Uffink citation

As an example, let's update the prior from Figure~\ref{fig:distribution}
using the testable information $\left<(x - 5)^2\right>_p = 1$.

\subsection{The ``constraint rule'' controversy}
Is it valid to use an experimental average (literally the arithmetic mean of
some data) to set the expected value of a probability distribution? The
assumption that this is okay has been termed {\it the constraint rule}.

@@

\bibitem[Knuth and Skilling(2010)]{2010arXiv1008.4831K} Knuth, K.~H., 
Skilling, J.\ 2010.\ Foundations of Inference.\
Axioms 1.1 (2012): 38-73.\
ArXiv e-prints arXiv:1008.4831. 
\end{thebibliography}

>>>>

As an example, let's update the prior from Figure~\ref{fig:distribution}
using the testable information $\left<(x - 5)^2\right>_p = 1$. The appropriate
value of the lagrange multiplier is $\lambda=0.5163846$, and the posterior is
shown in Figure~\ref{fig:distribution3}.
\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{distribution3.pdf}
\caption{\label{fig:distribution3}}
\end{center}
\end{figure}

\subsection{The ``constraint rule'' controversy}
Is it valid to use an experimental average (literally the arithmetic mean of
some data) to set the expected value of a probability distribution? The
assumption that this is okay has been termed {\it the constraint rule}
\citep{uffink}.

@@

\bibitem[Knuth and Skilling(2010)]{2010arXiv1008.4831K} Knuth, K.~H., 
Skilling, J.\ 2010.\ Foundations of Inference.\
Axioms 1.1 (2012): 38-73.\
ArXiv e-prints arXiv:1008.4831.

\bibitem[Uffink(1996)]{uffink} Uffink,~J. ``The constraint rule of the maximum entropy principle.'' Studies in History and Philosophy of Science Part B: Studies in History and Philosophy of Modern Physics 27.1 (1996): 47-79.
\end{thebibliography}
